# {ggplot}

All chapters start with a first-level heading followed by your chapter title, like the line above. There should be only one first-level heading (`#`) per .Rmd file.

## Break Legend Into Multiple Lines

You can use the `guides()` function to split your legend into multiple rows (`nrow` argument)

```{r }
library(survminer)
library(survival)
packageVersion("survminer")
packageVersion("survival")
```

```{r }
fit <- survfit(Surv(time, status) ~ ph.ecog, data = lung)

ggsurvplot(fit, data = lung) +
  guides(color = guide_legend(nrow = 2))

```

## Change Title of Legend

Change the title of any legend (e.g. fill, color, alpha) with `labs()`

```{r}
library(ggplot2)
packageVersion("ggplot2")

ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species,
                 alpha = Sepal.Width)) +
  geom_point() +
  labs(color = "Flower Species", 
       alpha = "Width of Sepal")


```

## Rotate X Axis 90 Degrees

```{r}
library(ggplot2)
packageVersion("ggplot2")

q <- ggplot(iris, aes(Species, Sepal.Width, fill = Species)) +
  geom_boxplot() 

q + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

